\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-29 body.tex
Update STLC example in 3.1
Update propositional partial recursor Update intro with structure and contribution.
intro tweak
Move sec3.1 ~> sec3, sec3.2~>sec 4.
Save, rewriting meta-theory
syntactical → syntactic

        FRecursor, MetaData, EndMetaData, Closing, Final, Inherit

@@

\section{Language Design}
% what feature we want
% what problem/formalization we want to achieve
% Before/After Comparison of examples (with/without Fampoly)
\label{sec:lang-design}
\input{lang-design.tex}

@@

@@

@@

For syntactical translation, please check \\ \href{https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing}{https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing}. This is the first QIIT-model we give. A QIIT-model can be consider as an arbitrary mapping from the QIIT data(our syntax in this case), also respecting the quotient(judgemental equality in this case). Here we use (a subpart of) QIIT data itself as the destination of the mapping.

>>>>

        FRecursor, MetaData, EndMetaData, Closing, Final, Inherit, FTheorem

@@

\section{Background and Challenges}
% what feature we want
% what problem/formalization we want to achieve
% Before/After Comparison of examples (with/without Fampoly)
\label{sec:background+challenge}
\input{challenge.tex}

@@

\section{Language Design}
% we need to make this section before Metatheory
% because a lot of our formulation in the metatheory
%   is inspired by the implementation
\label{sec:lang-design}
\input{lang-design.tex}

@@

It is hard to write modular, extensible code and proofs.
We have presented ...

@@

For syntactic translation, please check \\ \href{https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing}{https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing}. This is the first QIIT-model we give. A QIIT-model can be consider as an arbitrary mapping from the QIIT data(our syntax in this case), also respecting the quotient(judgemental equality in this case). Here we use (a subpart of) QIIT data itself as the destination of the mapping.

### 2022-07-29 syn-translate.tex
syntactical → syntactic

The implementation described in \cref{sec:coqimpl} can be formalized in our metatheory. The described compilation strategy can be considered as a \textit{syntactical translation}, a function mapping from our syntactical (QIIT-)model to a ``subpart''\footnote{Not exactly subpart---the only difference lies in the "Wrec", in our metatheory, it is constructed using linkage; in ``subpart'', it will be using sigma types (translation of the linkage).} of our syntactical (QIIT-)model \textit{without linkages}.\footnote{Here, syntactical QIIT-model can be roughly understood as just AST, with equational rules acting like quotient. So this mapping is mapping AST to AST, respecting quotient/judgemental equality.} This ``subpart'' is the standard MLTT with inductive type signature, a (non-conventional) W-type and a recursor that using sigma type to aggregate the handlers.

@@

The main idea of this syntactical translation is that, we make sure $\goodSig{\Gamma}{\nu^+ \_ }{n+1}$ and $\goodSig{\Gamma}{\mu^+ \_}{n+1}$ wrapped into a dependent pair. These two definitions decide the syntactical translation for $\goodSig{\Gamma}{\_}{n}$ and $\cL$. The syntactical translation for $\cC$ and $\cCt$ are decided by their $\beta$-rules.

@@

After syntactical translation, we can directly have consistency and canonicity \textit{if we assume the consistency and canonicity of the ``subpart''}. However, due to our non-conventional formulation of the inductive type, it is better we don't impose such assumption and directly give a consistency and canonicity proof.

% the link for syntactical translation
% https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing

>>>>

The implementation described in \cref{sec:coqimpl} can be formalized in our metatheory. The described compilation strategy can be considered as a \textit{syntactic translation}, a function mapping from our syntactic (QIIT-)model to a ``subpart''\footnote{Not exactly subpart---the only difference lies in the "Wrec", in our metatheory, it is constructed using linkage; in ``subpart'', it will be using sigma types (translation of the linkage).} of our syntactic (QIIT-)model \textit{without linkages}.\footnote{Here, syntactic QIIT-model can be roughly understood as just AST, with equational rules acting like quotient. So this mapping is mapping AST to AST, respecting quotient/judgemental equality.} This ``subpart'' is the standard MLTT with inductive type signature, a (non-conventional) W-type and a recursor that using sigma type to aggregate the handlers.

@@

The main idea of this syntactic translation is that, we make sure $\goodSig{\Gamma}{\nu^+ \_ }{n+1}$ and $\goodSig{\Gamma}{\mu^+ \_}{n+1}$ wrapped into a dependent pair. These two definitions decide the syntactic translation for $\goodSig{\Gamma}{\_}{n}$ and $\cL$. The syntactic translation for $\cC$ and $\cCt$ are decided by their $\beta$-rules.

@@

After syntactic translation, we can directly have consistency and canonicity \textit{if we assume the consistency and canonicity of the ``subpart''}. However, due to our non-conventional formulation of the inductive type, it is better we don't impose such assumption and directly give a consistency and canonicity proof.

% the link for syntactic translation
% https://drive.google.com/file/d/1pMqn8DS4T4jiCubzk3HgMANjrfKpcGlI/view?usp=sharing
